Next Trippy Structures\thanks{Supported by organization x.}

### 2018-12-12 paper.tex
Definitions v1

\usepackage{marginnote}

@@

\section{Proposed Structures}
\subsection{Common Structures}
All boring style except for \texttt{initialTimes}, which is compressed with sampled ZSTD.

@@

We use three complementary structures to represent each component of the sequence:
\begin{itemize}
    \item CSA with special and circular $\$$
    \item lines WM "forest"
    \item jcodes WM
\end{itemize}

This construction allows us to answer from x to y with just CSA.

Then we can use WM forest to restrict lines.

And finally we can restrict times by finding out the right jcodes.

>>>>

\usepackage{enumerate}
\usepackage{marginnote}

@@

\subsection{A model for compact trip representation}
So here goes a picture where we have stops $s \in S$, lines $l \in L$ and journeys $j^l \in J^l$. Will possibly redefine to make clear that they are not sets, and then have subindexes like $s_i$ or $j^l_i$.

Users can be attached to trips, but we don't care about them yet.

\section{Proposed Structures}
\subsection{Common Structures}
We represent the network like this:

\begin{itemize}
    \item $lineStop_l(i)$ is the $i$th stop of line $l$
    \item $stopLine_s(i)$ is the $i$th line that makes a stop at the stop $s$
    \item $avgTime_l(i)$ is the average time in seconds that it takes for a vehicle of line $l$ to reach its $i$th stop from the start of a journey
    \item $initialTime_l(i)$ is the starting time of the $i$th journey for line $l$
\end{itemize}

All boring style except for \texttt{initialTimes}, which is compressed with sampled ZSTD.

@@

We use three complementary structures to represent each component of the sequence:
\begin{enumerate}[(i)]
    \item CSA with special and circular $\$$
    \item lines WM "forest"
    \item jcodes WM
\end{enumerate}

This construction allows us to answer from x to y with just (i).

Then we can use (ii) to restrict lines.

And finally we can restrict times by finding out the right jcodes and filtering through (iii).
